RadLib: a radiative property model library for CFD

### 2021-07-25 submissions/CPC_response_to_reviewers.md

Considering all these, I think that this CPiP submission is definitely within the scope of the journal and of interest to the research community. However, the following concerns must be addressed before the submission is considered for publication.

**The authors thank the reviewer for their insightful comments and suggestions. As members of the combustion community, we heartily agree that a tool like RadLib could benefit researchers and facilitate radiation model development for combustion CFD.**

1) I could not successfully build and run the library in two different Linux systems. In both cases, first, the cmake returned an error:
"CMake Error at c++/CMakeLists.txt:34 (install): install TARGETS given no ARCHIVE DESTINATION for static library target "radlib"."
I could resolve this by adding ARCHIVE DESTINATION line on the c++/CMakeLists.txt file.
But, then on during "make" my installation was interrupted several times because of missing packages in my Python installation.
I would strongly recommend that the authors modify the installation instructions to include: a) list of dependencies (i.e., what compilers, what versions of python, what python packages, etc.), b) how to install the dependencies before building RadLib, c) a way to build RadLib with either only C++ or only Python. These installation notes do not necessarily need to be in the main manuscript, but they must be in the installation README of the code package.

	**The CMake build system has been updated such that ```ARCHIVE DESTINATION``` is explicitly specified, so that error should no longer occur. A build option has been added that makes the Python interface installation optional. Note that the C++ source code is required to install the Python interface, so there is no option to build only the Python interface. This information has been added to the ```README.md``` files located in the root directory and the ```build``` directory along with a more thorough list of software dependencies and required Python packages. We have also done full tests of the installation and running of all examples on a desktop Mac, and a desktop Linux machine. The c++ and fortran interfaces were tested on a large Linux-based cluster. The code also runs on a code ocean module.**

### 2021-07-25 submissions/CPC_response_to_reviewers.md

    3. These kinds of statements persist throughout the second paragraph as well. There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc. The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.

    **In the first sentence and paragraph of Section 5, "radiative heat transfer models" does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole. This generalization was intended for the entire first paragraph of Section 5.**

    **Regarding solution of the RTE versus the radiative property model, the reviewer is correct that in most engineering calculations, specification and implementation of the RTE can be more complex and costly than that of the property model. For both parts, however, this depends strongly on the particular model used, (and the geometry considered). The optically-thin model RTE model is trivial, and the RCSLW property model is not. We revised the manuscript to include a discussion of this in the second paragraph of the introduction, with a specific note that "In practical engineering simulations, the solution of the RTE is often the most complex and costly part of radiative simulation..." That said, we believe that access to good radiative property models as presented in this paper is a valuable contribution.**

    **We want to be careful with what is claimed in the paper, and some major revision has occurred in response to this reviewer's comments and others. Section 4 contained examples provided along with results, but now contains a description of the examples provided with the code. Section 5 contained some discussion items as noted by the reviewer, but now includes simulation results for the examples along with a CFD demonstration. The discussion items noted by the reviewer have been modified and folded into the Conclusions section.**

@@

3. Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement. See comments below w.r.t. assumptions on species considered, hard-coded polynomial coefficients, etc. all of which reduce extensibility.

    **We remove the word "modular" throughout the paper. We do believe that the library can be extended, and have noted this, with softer language, in the revision. The reviewer is correct that we do not provide explicit functionality, for, e.g., generic extension to other species. In some cases, like the PM model, such extension would be trivial within the existing code structure. In the RCSLW model, extension to other species would require provision of the species ALBDF (not trivial), and then extension would be a straightforward, but the code is not set up for arbitrary species in arbitrary order. The library is primarily targeted at combustion applications where CO2 and H2O are the primary radiative species. Future efforts may motivate further extension.**

@@

		**This has been corrected.**

### Software deficiencies & suggestions:

1. API doxygen documentation is non-standard. It appears that the doxygen documentation is provided in the .cc files rather than the header files, which is where it is typically found. Downstream developers would typically be working from headers and the installed library, so it is convention to have doxygen documentation in the header only. This also reduces clutter in the implementation files.

**We believe this to be a stylistic preference. Here's a quote from the [doxygen website](https://www.doxygen.nl/manual/docblocks.html): "Unlike most other documentation systems, doxygen also allows you to put the documentation of members (including global functions) in front of the definition. This way the documentation can be placed in the source file instead of the header file. This keeps the header file compact, and allows the implementer of the members more direct access to the documentation." Furthermore, Doxygen is primarily used to build external documentation (html), so, from that perspective, it does not seem as important where the Doxygen comments are in the source code.
The reviewer's argument makes more sense for libraries that are distributed without the source. In our case, we provide the source and the header files. We follow the approach of putting class comments, data member documentation, and class usage in the header, and documentation of how the methods/functions work in the source files where they are defined. This has the benefit of not cluttering the header files. There certainly is some precedence for this in online discussions.**

@@

2. make_examples.sh:
    1.	will only work with a g++ compiler in the user’s path.
    1.	Is referred to as build_examples.sh in the README.md file
    1.	is redundant with the cmake build system and isn’t portable. It should probably be removed.

	**The ```make_examples.sh``` file has been removed and examples are built with CMake. This script was originally included for reference.**

3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.

    **The API is pretty simple and consists of two functions. Extensive examples are provided, which are compared to LBL data, and which, as published here, are identical to the results of the published radiation models. That said, a branch of the code is being developed that includes tests.**

@@

    3.	Using GLOB to install the headers is not the appropriate CMake approach.

		**The build updated accordingly; GLOB is no longer used to install header files.**

    5.	the data files are not copied into the examples build directory, meaning that the example executables do not run.

        **The original code has been updated and tested and this is now corrected.**

@@

    3.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...

		**Build target name has been changed from "doxygen" to "docs" for safety. Note that building the documentation is off by default.**

5. It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker.

    **This is true. The code is not presently set up to load HITEMP/HITRAN data. This is a good suggestion and we would like to extend the model to allow LBL simulations in the future.**

@@

6. It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits? Same for WSGG. There is no discussion of why this was chosen, how the coefficients were determined, or a characterization of its accuracy. Do you observe any problematic behavior with the fourth order polynomials over temperatures from 300 to 3000 K?  Are these interpolants or regression of data?

    **The software implements the PM and WSGG models as provided in the cited references, which use polynomial fits. Model details are noted in the cited references. Use of a polynomial fit is standard for WSGG models, and a polynomial fit to temperature for species for the PM model seems reasonable. The PM model used is the one advocated by the TNF workshop cited in the paper, which is standard in the combustion community. The temperature range is 300-2500 K for the PM model. This is now stated in the paper, and the code enforces this range. The range for the WSGG model is 300-2400 K. The range for the RCSLW model is 300-3000 K. Temperatures outside these bounds use these bounds for the WSGG and RCSLW models. This is now stated in the paper.**

7. The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits. And given that this process is opaque, it isn’t reproducible.

    **The implemented models described in the cited literature. The novelty of the presented library is not the development of the absorption models, but the implementation, validation, and documentation of a library for application. Using RadLib to generate correlations for species using HITEMP/HITRAN is outside of the intended scope. We acknowledge that extra work is required to extend the models to additional species, or to extend the temperature ranges. However, the species included cover a very wide range of practical applications, certainly in the combustion field, and models for other species (e.g., for WSGG, and RCSLW) are often not available. Indeed, Bordbar's WSGG model is one of the few (if not the only one) that is provided for arbitrary compositions of CO2 and H2O, with others assuming fixed or limited ratios. That said, radlib is documenented and while the code does not provide extension machinery directly, extending to additional species by following the existing code structure would not be difficult if such data/correlations were available.**

@@

8. RadLib only considers CO2 and H2O for WSGG, which is fairly limited. Even for Plank mean, only H2O, CO2, CO and CH4 are considered. NO and OH would be nice to include. It appears that including additional species would be a non-trivial undertaking.

    **See our reply to the previous comment regarding additional species. For heat transfer applications in combustion, NO and OH are minor species and will not contribute in any meaningful way. CO2, H2O, and soot will drive the radiation in practical configurations. It would be nice to include CO in the WSGG model, and we would like to do this following Bordbar's approach. But even CO is a minor species compared to CO2, both in terms of its concentration in practical systems (usually), and it's asorption coefficient on an equal concentration basis. CH4 was only included in the PM model from the TNF workshop since many of the fuels used there include CH4. But CH4 will largely be present at relatively low temperatures, not the highly radiating flame zones.**

	**We note that major revisions have been made to the paper text to clarify points like these for readers who do not specialize in, e.g., combustion processes or modeling and provide additional information about why these models were chosen for implementation in RadLib.**

@@

9. Documentation:
    1.	Generating the documentation directly via doxygen v. 1.8.20 gives numerous warnings about obsolete tags and then fails because it is looking for a relative path “../../docs/doxygen” that doesn’t exist. This should be fixed.
    1.	Generating the doxygen documentation via the build system target (“make doxygen”) does seem to work fine.

	**The build process has been updated so that documentation can be generated by the system target or manually by running the command ```doxygen``` in the docs folder. We have removed obsolete flags, and also updated the source documentation to be consistent with function signatures.**

@@

----------------------------------------------------

## Reviewer 2

A radiation spectral property library is developed in this study using C++. A Planck-mean absorption coefficient based model, a WSGG model and a RCSLM model from the literature are implemented  in the package. Verification results are presented and discussed. Although the authors addressed an important issue of radiation modeling, the contribution is marginal in the reviewer's opinion. No new models/methods are proposed in this study. As the authors correctly pointed out, the solver for radiative transfer equation is equally important, which is not included in the library. The coupling of a spectral model to a specific RTE solver, can have different levels of challenges depending on the combination. The design of the library doesn't really address any of the RTE-related issues, nor provide any new solutions to simplify the coupling of spectral models to RTEs. If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE solvers such as P1 and DOM, it would further improve the quality of this study. A few other concerns are listed as follows:

**The authors thank the reviewer for their comments and suggestions. It is true that the library presented does not develop new models, but implementing and providing those models is nontrivial, and we believe makes a good contribution that is within the scope of this software journal.**

@@

	**The absorption coefficients for the gray gases are developed from high resolution databased, and correlated, for each gray gas considered, as functions of the local gas state (temperature, pressure, and composition). The PM model uses a temperature correlation for each species absorbtion coefficient, with the overall absorption coefficient computed by combining the species. The WSGG model uses correlations developed for the gray gases based on emmivity calculations from the high resolution databases, and treats the composition through the molar H2O/CO2 ratio. The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using spectral data available from databases like HITEMP. See Solvjov 2017 (cited in the paper) for details. The revision includes such discussions for the individual models. The modification of the original statement is in the last paragraph in Section 2 before section 2.1.**

7) On page 7, the authors mention that the PM model can be "reasonably accurate" in some cases and go on to say that, "The Planck Mean model is most appropriate under optically thin conditions  with  relatively  low  radiative  transfer  relative  to  other  heat  sources such  as  reactive  heat  release  rates." The Planck Mean model will be appropriate in optically thin cases as there is very little reabsorption. This may or may not be connected with "relatively  low  radiative  transfer  relative  to  other  heat  sources." In fact, if the radiative heat transfer is much lower than chemical heat release, neglecting radiation altogether may also be reasonable! Although, the definition of "relatively low" is subjective.

    **This discussion is modified in the revision. The PM model is not directly connected to optical thickness of flames. In combustion applications, the PM model is often used in situations that are optically thin. In such cases, the radiative losses are relatively low (often around 5% for laboratory jet flames), and use of the PM model may provide sufficient accuracy given that errors are active at the 5% level of the overall radiative losses, so not severe. When coupled with the optically thin assumption for RTE treatment, the radiative solve is relatively simple and inexpensive.**

### 2021-07-25 manuscript/manuscript.tex
DOL: removing commented lines from the manuscript
spelling

\title{RadLib: a radiative property model library for combustion CFD}

@@

Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem. Combustion is one of the key radiative tranfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures \citep{Modest_2016}. Additionally, some late-stage flame phenomena, particularly soot behavior and flamesheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the RadLib library, which implements three radiation property models, with C++, Python, and Fortran interfaces, and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.

@@

With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with optional Python and Fortran interfaces. RadLib calculates radiation absorption coefficients and weighting factors for use in global radiation models. Expansion to other radiative properties and model types is possible. Three models are fully implemented and validated. 
%All models use a common interface to facilitate researchers' access to and use of radiation modeling tools suitable for combustion CFD applications.

@@

At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model. These models were chosen for their relavance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

%Absorption coefficients and other radiative property data may take on different forms depending on the RTE solution approach, but can generally be classified as either spectral (wavenumber-dependent) or global (integrated over wavenumber). Spectral absorption coefficients can be applied to the spectral RTE (Eq.~\ref{e:RTE_general}), while global absorption coefficients are used in the spectrally-integrated RTE (Eq.~\ref{e:RTE_wsgg}). The type of absorption coefficient generated by each model and potential RTE integration strategies will also be discussed in the following sections. While solving the RTE is not the focus of this software, RadLib's example cases do employ a simple ray tracing solver to calculate the radiative heat flux and volumetric heat source profiles between two parallel planes. Refer to the example cases in Section \ref{s:Examples} for details.

@@

The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation. Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss. It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%. At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate. 
% todo: show the RTE equation/source term

%Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}. The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K. TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}.

%RadLib's simplest radiation property model generates Planck Mean absorption coefficients under the assumption of optically thin media, from here on referred to as the Planck Mean (PM) model.
%The optically thin approximation assumes that there is little to no reabsorption of radiative energy in the system, or, in other words, that the system only emits radiation and does not absorb it. In combustion systems, optical thinness is associated with various other flame properties such as low radiative heat transfer relative to chemical heat release or convective heat transfer, negligible amounts of soot or other large molecules, and relatively small flame lengths. These flame attributes are not universally indicative of optical thinness, but are often used to justify neglecting or simplifying radiative heat transfer modeling. Assuming optical thinness, however, has the distinct advantage of simplifying the radiative source term (denoted $S_{rad}$) of the energy conservation equation to 
%\begin{equation}
%	S_{rad}=-4\kappa \sigma T^4,
%\end{equation}
%where $\kappa$ is the radiation absorption coefficient, $\sigma$ is the Stefan-Boltzmann constant, and $T$ is temperature. Using an optically thin approximation means that no RTE solution is required when calculating radiative source terms.
%
%In combustion systems, this simplification is convenient because it makes radiation modeling easy to implement and computationally inexpensive. The vast majority of computational combustion research that considers radiation employs an optically thin approximation despite its limited applicability to combustion processes. Assuming optical thinness can predict the radiative behavior of small laboratory flames reasonably well, but in larger flames or industrial systems tends to overpredict radiative heat losses by 50\% or more and underpredicts flame temperatures by over 100$^{\circ}$C \citep{Modest_2016}. 
%
%The specific correlations for the Planck Mean absorption coefficients generated by RadLib come from the Turbulent Nonpremixed Flame (TNF) Workshop, an ongoing collaboration between experimental and computational researchers in turbulent combustion \citep{Smith_2003,Barlow_2001}. These particular correlations were chosen for RadLib's PM model because of the popularity and widespread use of the TNF Workshop radiation model in combustion research despite its limitations. Its temperature-dependent correlations are based on the RADCAL database \citep{Grosshandler_1993}, which has been largely superseded by more comprehensive and accurate databases, particularly HITRAN and HITEMP \citep{Rothman_2010}. The absorption coefficient correlations use fourth or fifth order polynomial fits in the range 300-2500 K. TNF Workshop literature shows that in cases where the optically thin approximation accurately describes the system, such as in simple hydrogen jet flames, the PM model produces accurate results \citep{Barlow_1999}. In cases where the optically thin assumption is not reasonable, however, including most practical combustion scenarios of interest to scientists and engineers, the PM model does not produce accurate results, overpredicting radiative heat loss and underpredicting flame temperature by 100$^{\circ}$ or more \cite{Frank_2000,Zhu_2002,Coelho_2002}. 
%
%Because of these limitations, the authors strongly recommend that RadLib users carefully consider the implications of the PM model before using it in combustion simulations. 
%It is implemented in RadLib primarily for comparison and evaluation against other radiation property models because of its popularity and widespread use. 
%The examples included with the RadLib code and shown in Section \ref{s:Examples} demonstrate the deficiencies of the PM model in comparison to other radiation property models included with RadLib.

@@

The RCSLW model uses rank correlation as follows.
Consider Eq.~\ref{e:albdf} evaluated at an arbitray reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
% $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
%
\begin{linenomath}
    \begin{align} \label{e:albdf2}
        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_2}E_b(\eta,T_r)d\eta.
    \end{align}
\end{linenomath}
%
Since $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are rank correlated (by definition), $H_1=H_2$ and we have 
%
\begin{linenomath}
    \begin{equation}\label{e:FeqF}
    F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
\end{equation}
\end{linenomath}
%
Recall that the ALBDF can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are known, we can compute $F=F(\hat{C}_1,\BS{\phi_1},T_r)$ and then invert $F$ to obtain $\hat{C}_2$ at $\BS{\phi}_2$. Note that Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$, so any known $F=F(C,\BS{\phi},T)$ can be inverted to get $C$ at the corresponding state $\BS{\phi}$.

@@

In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m. 
In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36~m in the thick and thin layers, respectively. These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
%, which coincides with the PM model's use of the optically thin approximation, but the high error in its predictions of radiative heat flux relative to the LBL data indicates that neither the optically thin approximation nor absorption coefficients calculated with this model are accurate for this case. 
Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}. %illustration of the PM model's deficiencies as discussed in Section~\ref{s:planckmean}: the PM model overpredicts radiative heat loss at the high temperatures that characterize most combustion processes.

@@

%The WSGG model gives somewhat accurate but inconsistent results for the example cases considered here. In Examples S1, S3, S5, B3, and Sb1, it behaves as expected, producing results that are closer to the LBL data than those produced by the PM model but fall short of the RCSLW model's level of accuracy. In general, the WSGG model appears to perform best at intermediate temperatures and deviates from the desired behavior at boundary conditions, but this is not universal. For example, the WSGG model shows uncharacteristically high accuracy in Example S2; its results with four gray gases are comparable in accuracy to the RCSLW model's performance using eight or more gray gases. In contrast, the WSGG model performs exceptionally poorly in Example S4, in which it deviates from the LBL data by nearly an order of magnitude at its largest. 
%The WSGG model, alongside with the PM model, is primarily empirical and contains little to no representative physics, which could explain the unexpected behavior in Examples S2 and S4. Given that all of the example cases use parameters within those specified for the WSGG model in the literature \cite{Bordbar_2014,Bordbar_2020}, neither anomalous result has an obvious source. While we cannot offer an explanation for the WSGG model's inconsistent performance, it serves to underscore the importance of individual model validation on a case-by-case basis, a task potentially made easier with tools like RadLib.

%The RCSLW model displays the most accurate results of the three implemented property models when compared to LBL data, capturing the relevant trends without exaggerating them. It is, however, the most difficult of the three models to implement and requires either correlated or tabulated spectral data to draw from. 
%The RCSLW model can be sensitive to the number of gray gases used, illustrated in Figure~\ref{f:examples} by Examples S2 and S5. The difference in accuracy between $n=2$ and $n=8$ gray gases is small for all of the example cases and typically falls within the margin of error represented by the WSGG model's deviation from the LBL data. Example S2 shows the most prominent variations in predicted radiative heat flux based on changes in the number of gray gases, improving drastically in agreement to the LBL data with the addition of just four gray gases. RCSLW model convergence can also vary with the value of the chosen reference temperature; in Example S5, for instance, the RCSLW model converges to the LBL data if it is initialized with the maximum rather than the average temperature on the domain. When treated properly, however, the RCSLW model provides the most accurate results of all of the radiation property models considered here.

Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas. Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data. In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species. Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.
%The agreement produced by RadLib's approach to soot radiation in Example Sb1 is an encouraging step toward accurate, detailed treatment of soot's radiative properties in complex combustion simulations.

@@

Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver. This is relavant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evalations alone. This is consistent with the results of the figure and as follows. Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively. 
%In running Example S3, the overall solution cost using different property models is shown to vary much less than when evaluating gas properties alone due to the additional overhead of the ray-tracing solver in performing the calculations.

@@

In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation. Results are compared to line-by-line (LBL) solutions. In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost. %Under appropriate conditions, the WSGG model can also produce accurate results at significantly lower computational cost, but may perform inconsistently under certain conditions. In general, the PM model is adequate in situations to which the optically thin approximation can be reasonably applied, but does not produce accurate results in any of the example cases presented here.

RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for relatively high temperature CFD applications, such as combustion, but could potentially be applied to research problems involving radiative heat transfer in other fields as well. RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models. Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions. By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations. %With RadLib, we believe that researchers will be able to put more of their time and effort into meaningful results rather than code or model development for radiative heat transfer in combustion CFD.

>>>>

\title{RadLib: a radiative property model library for CFD}

@@

Modeling radiative heat transfer in participating media in high temperature systems is a challenging problem. Combustion is one of the key radiative transfer applications, and combustion CFD is uniquely challenging because it involves numerous tightly coupled physical phenomena---including multicomponent mass transfer, convective and radiative heat transfer, turbulent fluid dynamics, multi-phase and particle flows, and complex chemical reaction kinetics---that span many orders of magnitude in both length and time scales. Combustion simulations are often complicated by a lack of accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost. Frequently, radiative heat transfer modeling in combustion systems is either neglected or oversimplified, resulting in significant errors flame temperatures \citep{Modest_2016}. Additionally, some late-stage flame phenomena, particularly soot behavior and flamesheet breakthrough, increasingly depend on and influence the magnitude of radiative heat losses and are difficult to simulate accurately without robust radiation modeling \cite{Modest_2013}. These problems motivated development of the RadLib library, which implements three radiation property models, with C++, Python, and Fortran interfaces, and provides a framework for additional models and further development, giving researchers convenient access to advanced radiation property modeling tools.

@@

With RadLib, we aim to provide researchers with a convenient access point for radiative property models that can be interfaced with various RTE solution approaches suitable for CFD applications. RadLib is a C++ library with optional Python and Fortran interfaces. RadLib calculates radiation absorption coefficients and weighting factors for use in global radiation models. Expansion to other radiative properties and model types is possible. Three models are fully implemented and validated.

@@

At present, RadLib includes three radiation property models of varying complexity: Planck Mean absorption coefficients using the optically thin approximation, a weighted sum of gray gases (WSGG) model, and the rank-correlated spectral line weighted-sum-of-gray-gases (RCSLW) model. These models were chosen for their relevance to practical radiative heat transfer simulations. They represent increasing levels of complexity, computational cost, and accuracy. Each model is discussed in more detail in the following sections.

@@

The PM model is often used in conjunction with the optically-thin approximation for solving the RTE, in which case the radiative source term of the energy transport equation is particularly simple, and the overall computational cost of the radiative treatment is negligible in comparison to other aspects of a reacting flow simulation. Many smaller combustion applications are radiatively thin, and have smaller radiative heat loss. It is not uncommon for non-sooting laboratory-scale research jet flames to have radiative losses of around 5\%. At these levels, the accuracy of the radiative property model is not as crucial, and simpler models like the PM model are appropriate.

@@

The RCSLW model uses rank correlation as follows.
Consider Eq.~\ref{e:albdf} evaluated at an arbitrary reference temperature $T_r$ for thermodynamic states $\phi_1$ and $\phi_2$ as detailed above:
% $C=\hat{C}_1$, $\BS{\phi}=\BS{\phi}_1$, $T=T_r$, and again at$C=\hat{C}_2$, $\BS{\phi}=\BS{\phi}_2$, $T=T_r$, where $T_r$ is some reference temperature:
%
\begin{linenomath}
    \begin{align} \label{e:albdf2}
        F(\hat{C}_1,\BS{\phi}_1,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_1}E_b(\eta,T_r)d\eta, \\
        F(\hat{C}_2,\BS{\phi}_2,T_r) &= \frac{1}{\sigma T_r^4}\int_{H_2}E_b(\eta,T_r)d\eta.
    \end{align}
\end{linenomath}
%
Since $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are rank correlated (by definition), $H_1=H_2$ and we have 
%
\begin{linenomath}
    \begin{equation}\label{e:FeqF}
    F(\hat{C}_1,\BS{\phi}_1,T_r)=F(\hat{C}_2,\BS{\phi}_2,T_r).
\end{equation}
\end{linenomath}
%
Recall that the ALBDF can be inverted, so if $\hat{C}_1$ and $\BS{\phi}_1$ are known, we can compute $F=F(\hat{C}_1,\BS{\phi_1},T_r)$ and then invert $F$ to obtain $\hat{C}_2$ at $\BS{\phi}_2$. Note that Eq.~\ref{e:FeqF} holds for arbitrary states $\BS{\phi}_1$ and $\BS{\phi}_2$, so any known $F=F(C,\BS{\phi},T)$ can be inverted to get $C$ at the corresponding state $\BS{\phi}$.

@@

In general, the PM model performs poorly compared to the WSGG and RCSLW models and the LBL data. The results show that the PM model tends to exaggerate the trends displayed by the other models. The PM data mimics the shape of the other curves in Example S5 as well, but the curve is off-scale and omitted for clarity. For the PM model in Example S5, $Q$ varies from around -80~kW/m$^3$ at $x=0$ to a peak of 200~kW/m$^3$ at x=$1.5$~m and drops to~100 kW/m$^3$ at $x=2$~m. 
In Example S2, the PM value of $q(L)/\sigma T^4$ is off the scale at an essentially constant value of unity. The PM absorption coefficient is 27.4 atm$^{-1}$m$^{-1}$, which results in a calculated optical thicknesses of 0.09 and 0.36~m in the thick and thin layers, respectively. These values are small compared to the domain sizes greater than 0.5 m considered in Example S2.
Example S3 illustrates that the PM model tends to overpredict radiative heat loss at hight temperatures, which has been previously observed \cite{Frank_2000,Zhu_2002,Coelho_2002}.

@@

Figure~\ref{f:exSb1} shows the results from Example Sb1, which considers three magnitudes of the soot volume fraction in addition to the radiating gas. Both the WSGG and RCSLW models perform accurately in all three cases, but the PM model displays significant deviations from the LBL data. In sooting flames, soot acts as a significant source and sink of radiation, and its radiative properties differ significantly from those of the participating gaseous species. Soot reactions and transport are both sensitive to, and strongly influence local variations in, flame temperature and gas composition, forming a feedback loop in which accurate prediction of both gas and soot radiative properties becomes critical to predicting flame properties and behavior, particularly late-stage flame phenomena such as flame sheet breakthrough, smoke production, and extinction and reignition processes.

@@

Figure~\ref{f:cost}b shows the cost to evaluate Example S3, which involves both evaluation of the gas properties and solution of the RTE using the provided ray-tracing solver. This is relevant because radiative property calculations are rarely done in isolation, but are part of a larger RTE solution, so that overall cost differences may be smaller than those of the property evaluations alone. This is consistent with the results of the figure and as follows. Relative to the WSGG model, which required 0.0079 s, the model costs for the PM model and the RCSLW model with $n=1$, 2, 4, 8 gray gases was approximately 0.75, 1.1, 1.4, 1.9, and 2.9, respectively.

@@

In addition to the library itself, RadLib includes several illustrative example cases in a one-dimensional parallel planes geometry using a simple ray tracing solver to demonstrate use of the library and validate model implementation. Results are compared to line-by-line (LBL) solutions. In general, the RCSLW model outperforms both the PM and WSGG models in terms of accuracy at the expense of computational cost.

RadLib is intended as a convenient access point for researchers who require radiation property modeling tools for relatively high temperature CFD applications, such as combustion, but could potentially be applied to research problems involving radiative heat transfer in other fields as well. RadLib is designed to facilitate and simplify the process of implementing and/or using radiative property models; it consolidates various model types into a single library with a consistent framework, reducing some of the overhead associated with choosing, implementing, and testing radiation property models. Its framework can be used to implement and validate new models as well as compare existing models under consistent conditions. By facilitating model comparison through a common interface, RadLib can provide a practical means of testing specific modeling approaches without the restrictions imposed by large-scale CFD simulations.
